\documentclass[12pt,a4paper]{report}

% Custom styles
\usepackage{electronics}

% Bibliography
\usepackage[citestyle=authortitle,url=true]{biblatex}
\addbibresource{electronics.bib}

\begin{document}

When constructing the system, it is vital that all practical work is carried out
sfaely. To that end, precautions were taken against the following risks:

\begin{description}
  \item[Electrocution] No high voltage/current power supplies will be used (the
  highest voltage that may possibly be used will be \SI{15}{\volt}) so the
  danger is relatively low. Even so, appropriate precautions will be taken: the
  circuit will not be touched or modified when switched on and will not be
  placed near liquids.

  \item[Electrostatic damage] Many of the components used utilise CMOS
  technology so are very sensitive to electrostatic discharge. To minimise the
  risk of this happening, I will ground myself on a suitable surface (computer
  power supply case, grounded radiator, etc) before approaching the circuit.

  \item[Fire and/or burns] A number of components (e.g., the power supply diodes
  and chips) could potentially get extremely hot if misused. While I will
  obviously aim not to misuse them, accidents happen, and to this extent I will
  be careful and slow in touching any component in case it is hot enough to
  burn. Also, I will ensure no paper or other easily flammable materials are
  placed near the circuit.

  \item[Back injury] A number of components will need to be ordered from the
  internet, meaning they will come in large boxes. I will need to use proper
  lifting techniques when bending down and lifting these boxes to avoid back
  injury.

  \item[Cutting injuries] Throughout the course of the project I will be using
  various sharp tools, such as wire cutters. I will need to make sure I am
  trained in using these tools, that I concentrate when using them and that I
  leave them in a safe place so others do not accidentally injure themselves.
  These actions will help to reduce the risk of injuries.
\end{description}


\end{document}
